Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-06-29 doc/PRF2022/PRF_main.tex
updates
yny

% body of paper here - Use proper section commands
% References should be done using the \cite, \ref, and \label commands
\section{Introduction}
% Put \label in argument of \section for cross-referencing
%\section{\label{}}
The many-body hydrodynamics of amphiphilic Janus particles (JP) suspended in a viscous fluid (at zero Reynolds number) has been studied using
boundary integral numerical simulations \cite{Fu2022_JFM}. Janus particles consist of both a hydrophobic and a hydrophilic surfaces. 
Immersed in a viscous solvent, the dynamics of a JP suspension results from the combination of long-range hydrodynamic interaction and non-local
interactions between JPs through the distribution of a hydrophobic potential (HAP). In a quiescent flow, numerical simulations of a 
JP suspension showed self-assembly into micelles and bilayers of JPs that provide an alternative means for computing the 
mechanical moduli of a colloidal membrane.

@@

%\begin{figure}
%\caption{\label{fig:ves_shear} A vesicle in shear flow}
%\end{figure}
%\begin{figure}
%\caption{\label{fig:ves_shear} A vesicle in Taylor-Green flow}
%\end{figure}
\begin{figure}
  \begin{center}
  \includegraphics[width=0.3\textwidth]{VS_E.pdf}
   \includegraphics[width=0.3\textwidth]{VS_LOP.pdf}
    \includegraphics[width=0.3\textwidth]{VS_MSD.pdf}\\
      \includegraphics[width=0.3\textwidth]{BS_E.pdf}
   \includegraphics[width=0.3\textwidth]{BS_LOP.pdf}
    \includegraphics[width=0.3\textwidth]{BS_MSD.pdf}
  \end{center}
  \caption{
    \label{fig:BC1_shear}
    Comparisons between vesicle (top row) and bilayer (bottom row) configurations: Energy $E(t)$, local order parameter $\tilde{S}_2(t)$, and the mean square displacement $MSD(t)$. Shear rates are $\dot\gamma=\{0.05, 0.0655, 0.75\}$. The shear rate $\dot\gamma = 0.0655$ are picked from ~\cite{Fu2022_JFM} where it is known to be the critical shear rate for ruptures and the trend is clearly distinguished from all three measures. For the bilayer configurations, as shown in Fig~\ref{fig:relax}, multiple bialyer structures are placed in shear flows. The supplementary movies show that a slower shear flow results menbrane fusions and $\tilde{S}_2(t)$ increases in the long run.
     }
\end{figure}

@@

@@

\begin{figure}
  \begin{center}
  \includegraphics[width=0.4\textwidth]{VTG_Area}
  \includegraphics[width=0.4\textwidth]{VTG_Len}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:VTG_AreaLen} Vesicle in a Taylor-Green flow where $V_0=0.1$ and the size of rotating cell $l$ is varied. The enclosed area calculated from the bilayer midplane decreases over time and the total length measured from the midplane remains nearly constant with small magnitude of oscillations. }
\end{figure}

@@

>>>>

% body of paper here - Use proper section commands
% References should be done using the \cite, \ref, and \label commands
\section{Introduction}
% Put \label in argument of \section for cross-referencing
%\section{\label{}}
Janus particles are particles with two surfaces of different properties such as hydrophobicity. For example, it is common for a Janus particle to have a hydrophobic hemisphere and a hydrophilic hemisphere. In a viscous solvent Janus particles often self-assemble into structures of tunable functions for biomedical engineering applications \cite{GheisariSahfieeAbbasiEtAl2021_DMR,LiuYangHuangEtAl2016_Angew,LiWangYaoEtAl2019_Nanoscale}. Depending on the interactions between Janus particles and the surrounding viscous solvent, JPs self-assemble into oligomers of various geometries and sizes.

The many-body hydrodynamics of amphiphilic Janus particles (JP) suspended in a viscous fluid (at zero Reynolds number) has been studied using
boundary integral numerical simulations \cite{Fu2022_JFM}. Janus particles consist of both a hydrophobic and a hydrophilic surfaces. 
Immersed in a viscous solvent, the dynamics of a JP suspension results from the combination of long-range hydrodynamic interaction and non-local
interactions between JPs through the distribution of a hydrophobic potential (HAP). In a quiescent flow, numerical simulations of a 
JP suspension showed self-assembly into micelles and bilayers of JPs that provide an alternative means for computing the 
mechanical moduli of a colloidal membrane.

@@

@@

\begin{figure}
  \begin{center}
  \includegraphics[width=0.3\textwidth]{VS_E.pdf}
   \includegraphics[width=0.3\textwidth]{VS_LOP.pdf}
    \includegraphics[width=0.3\textwidth]{VS_MSD.pdf}\\
      \includegraphics[width=0.3\textwidth]{BS_E.pdf}
   \includegraphics[width=0.3\textwidth]{BS_LOP.pdf}
    \includegraphics[width=0.3\textwidth]{BS_MSD.pdf}
  \end{center}
  \caption{
    \label{fig:BC1_shear}
    Comparisons between vesicle (top row) and bilayer (bottom row) configurations: Energy $E(t)$, local order parameter $\tilde{S}_2(t)$, and the mean square displacement $MSD(t)$. Shear rates are $\dot\gamma=\{0.05, 0.0655, 0.75\}$. The shear rate $\dot\gamma = 0.0655$ are picked from ~\cite{Fu2022_JFM} where it is known to be the critical shear rate for ruptures and the trend is clearly distinguished from all three measures. For the bilayer configurations, as shown in Fig~\ref{fig:relax}, multiple bialyer structures are placed in shear flows. The supplementary movies show that a slower shear flow results menbrane fusions and $\tilde{S}_2(t)$ increases in the long run.
     }
\end{figure}

@@

@@

\begin{figure}
  \begin{center}
  \includegraphics[width=0.4\textwidth]{VTG_Len.pdf}
  \includegraphics[width=0.4\textwidth]{VTG_Area.pdf}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:VTG_AreaLen} Vesicle in a Taylor-Green flow where $V_0=0.1$ and the size of rotating cell $l$ is varied. The enclosed area calculated from the bilayer midplane decreases over time and the total length measured from the midplane remains nearly constant with small magnitude of oscillations. }
\end{figure}
